---
title: "Introduction to Keras"
author: "Dr Juan H Klopper"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd(getwd())
library(keras)
```

## Preparing the data

```{r}
mnist <- dataset_mnist()
```

```{r}
names(mnist)
```

```{r}
x_train <- mnist$train$x
y_train <- mnist$train$y
x_test <- mnist$test$x
y_test <- mnist$test$y
```

```{r}
dim(x_train)
```

```{r}
dim(y_train)
```

```{r}
# reshape
x_train <- array_reshape(x_train, c(nrow(x_train), 784))
x_test <- array_reshape(x_test, c(nrow(x_test), 784))
# rescale
x_train <- x_train / 255
x_test <- x_test / 255
```

One-hot encoding

```{r}
y_train <- to_categorical(y_train, 10)
y_test <- to_categorical(y_test, 10)
```

## Building the model

```{r}
model <- keras_model_sequential() 
model %>% 
  layer_dense(units = 256, activation = 'relu', input_shape = c(784)) %>% 
  layer_dropout(rate = 0.4) %>% 
  layer_dense(units = 128, activation = 'relu') %>%
  layer_dropout(rate = 0.3) %>%
  layer_dense(units = 10, activation = 'softmax')
```

A summary of the model can be viewed.  This shows the shape of each layer and the number of trainalble and non-trainable parameters.

```{r}
summary(model)
```

Next up is the compilation of the model, providing the loss function, the optimizer, and the metric to be displayed during each epoch.

```{r}
model %>% compile(
  loss = 'categorical_crossentropy',
  optimizer = optimizer_rmsprop(),
  metrics = c('accuracy')
)
```

## Training and evaluating

```{r}
history <- model %>% fit(
  x_train, y_train, 
  epochs = 30, batch_size = 128, 
  validation_split = 0.2
)
```

```{r}
plot(history)
```

## Evaluating on the test set

```{r}
model %>% 
  evaluate(x_test,
           y_test)
```

